Included  Summary (teaching-v2.0)

### 2020-12-15 experiment-2/analysis/preprocessor/included_summary.Rmd
update included_summary
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("here")) {install.packages("here"); require("here")}

# set working directory
here::i_am("included_summary.Rmd")

# read txt files
dt_ioi <- fread(file = here("trimmed", "data_ioi_1.txt"), sep = ",")
dt_kor <- fread(file = here("trimmed", "data_kor.txt"), sep = ",")
dt_kot <- fread(file = here("trimmed", "data_kot.txt"), sep = ",")
dt_vel <- fread(file = here("trimmed", "data_vel.txt"), sep = ",")
dt_vel_diff <- fread(file = here("trimmed", "data_vel_diff.txt"), sep = ",")
```

# Design
- Each performance (1 trial) contains 72 responses for onsets and 72 responses for offsets (i.e., if there is no mistake, 144 responses in total)
- Each block contains 8 trials and there are 4 blocks (teaching vs. performing x articulation vs. dynamics)
- Note: SubNr 3 was excluded due to insufficient motor skills

@@

### Export only included participants
data_analysis~.txt are used for data analysis.
```{r export, echo = TRUE}
fwrite(dt_ioi[SubNr != 3], file = here("trimmed", "data_analysis_ioi.txt"), sep = ",")
fwrite(dt_kor[SubNr != 3], file = here("trimmed", "data_analysis_kor.txt"), sep = ",")
fwrite(dt_kot[SubNr != 3], file = here("trimmed", "data_analysis_kot.txt"), sep = ",")
fwrite(dt_vel[SubNr != 3], file = here("trimmed", "data_analysis_vel.txt"), sep = ",")
fwrite(dt_vel_diff[SubNr != 3], file = here("trimmed", "data_analysis_vel_diff.txt"), sep = ",")
```

>>>>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}

# read txt files
dt_ioi <- fread(file = "./trimmed/data_ioi_1.txt", sep = ",")
dt_kor <- fread(file = "./trimmed/data_kor.txt", sep = ",")
dt_kot <- fread(file = "./trimmed/data_kot.txt", sep = ",")
dt_vel <- fread(file = "./trimmed/data_vel.txt", sep = ",")
dt_vel_diff <- fread(file = "./trimmed/data_vel_diff.txt", sep = ",")
```

# Design
- Each performance (1 trial) contains 72 responses for onsets and 72 responses for offsets (i.e., if there is no mistake, 144 responses in total)
- Each block contains 8 trials and there are 4 blocks (teaching vs. performing x articulation vs. dynamics)
- Note: SubNr 3 was excluded due to insufficient motor skills. SubNr 2 was excluded due to a deviated tempo.

@@

### Export only included participants
data_analysis~.txt are used for data analysis.
```{r export, echo = TRUE}
fwrite(dt_ioi[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_ioi.txt", sep = ",")
fwrite(dt_kor[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_kor.txt", sep = ",")
fwrite(dt_kot[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_kot.txt", sep = ",")
fwrite(dt_vel[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_vel.txt", sep = ",")
fwrite(dt_vel_diff[SubNr != 2 & SubNr != 3], file = "./trimmed/data_analysis_vel_diff.txt", sep = ",")
```
